Titeln på avhandlingens språk

### 2023-04-23 body/part1/chapter2-relatedwork/scope.tex
scope

@@

In this dissertation we introduce and study the applicability of an alternative methodology for Edge performance evaluation based on a practical, experimental approach.
We aim to complement literature by providing a method which bridges the gap in knowledge left by existing approaches.
Or work centers of Edge Computing environments involving latency-sensitive applications such as \gls{XR} and \glspl{CPS}, as these are broadly understood to represent ``killer'' use-cases for the Edge.
We also focus exclusively on Cloudlet Computing-like setups.
Although \gls{MEC} is one of the main enablers for \gls{WCA} applications, we consider such network deployments to be \gls{OOS} due to the complexity and financial investment required to deploy a mobile network.
Likewise, we do not target Fog Computing deployments due to this paradigm being a poor fit for latency-sensitive applications.
Thus, although the methodology and tools introduced are architecture-agnostic and should be directly applicable to other kinds of Edge Computing setups than the one used in this dissertation, further work may be needed to validate our results and conclusions in the context of \gls{MEC} and Fog Computing.

>>>>

\input{tables/scope}

@@

In this dissertation we introduce and study the applicability of an alternative methodology for Edge performance evaluation based on a practical, experimental approach.
We aim to complement literature by providing a method which bridges the gap in knowledge left by existing approaches.
Our work centers of Edge Computing environments involving latency-sensitive applications such as \gls{XR} and \glspl{CPS}, as these are broadly understood to represent ``killer'' use-cases for the Edge.
We also focus exclusively on Cloudlet Computing-like setups (see \cref{tab:scope}).
Although \gls{MEC} is one of the main enablers for \gls{WCA} applications, we consider such network deployments to be \gls{OOS} due to the complexity and financial investment required to deploy a mobile network.
Likewise, we do not target Fog Computing deployments due to this paradigm being a poor fit for latency-sensitive applications.
Thus, although the methodology and tools introduced are architecture-agnostic and should be directly applicable to other kinds of Edge Computing setups than the one used in this dissertation, further work may be needed to validate our results and conclusions in the context of \gls{MEC} and Fog Computing.

### 2023-04-23 body/part1/chapter2-relatedwork/tables/scope.tex
scope

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
    \centering
    \caption{Overview of the scope and main contribution of each included publication.}\label{tab:scope}
    \tiny
    \renewcommand{\arraystretch}{1.5}
    \begin{tabularx}{\textwidth}{@{}ccXYX@{}}
        \toprule
        \textbf{Paper} & \textbf{Application} & \textbf{Emulation Approach} & \textbf{Network} & \textbf{Main Contribution}                                \\ \midrule
        \ref{paper:olguinmunoz2018demoscaling} & \acs{WCA} & Trace, \acs{FSM} user model & Wi-Fi & Initial demo of methodology. \\
        %
        \ref{paper:olguinmunoz2019edgedroid} & \acs{WCA} & Trace, \acs{FSM} user model & Wi-Fi & EdgeDroid tool for application of the methodology to \acs{WCA}. \\
        %
        \ref{paper:olguinmunoz2021impact} & \acs{WCA} & \acs{N/A} & No network & Characterization of human behavior in \acs{WCA}. \\
        %
        \ref{paper:olguinmunoz2022cleave} & \acs{NCS} & Software implementation of Control System & Wi-Fi & \acs{CLEAVE} tool for application of the methodology to \acs{NCS}. \\
        %
        \ref{paper:olguinmunoz2022ainur} & \acs{WCA}, \acs{NCS} & \acs{N/A} & Ethernet, Wi-Fi, 4G~\acs{LTE} & Ainur framework for Edge Computing testbed automation. \\
        \ref{paper:olguinmunoz2023realistic} &
        \acs{WCA} &
        Data-driven stochastic synthetic trace and user model &
        Wi-Fi &
        Model for end-to-end emulation of humans in \acs{WCA}, exploration of implications of methodology and model for \acs{WCA} optimization. \\
        \bottomrule
    \end{tabularx}
\end{table}

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[]
    \centering
    \caption{Visualization of the scope of this dissertation with respect to performance evaluation.
    We focus exclusively on Edge Computing based on Cloudlets~\cite{satyanarayanan2009case} and on experimental performance evaluation of \gls{XR} and \glspl{CPS}.}
    \label{tab:scope}
    \begin{tabularx}{\textwidth}{@{}YYYY@{}}
        \toprule
        & {Analytical Modeling} & {Simulations} & {Experimental}                   \\ \midrule
        Cloudlets & \cellcolor[HTML]{9AFF99}Yes & \cellcolor[HTML]{9AFF99}Yes & \cellcolor[HTML]{9AFF99}{\color[HTML]{333333} Yes} \\
        \gls{MEC} & \cellcolor[HTML]{FFCCC9}No              & \cellcolor[HTML]{FFCCC9}No      & \cellcolor[HTML]{FFCCC9}No                         \\
        Fog & \cellcolor[HTML]{FFCCC9}No              & \cellcolor[HTML]{FFCCC9}No      & \cellcolor[HTML]{FFCCC9}No                         \\
        \gls{XR}  & \cellcolor[HTML]{FFCCC9}No              & \cellcolor[HTML]{FFCCC9}No      & \cellcolor[HTML]{9AFF99}{\color[HTML]{333333} Yes} \\
        \glspl{CPS} & \cellcolor[HTML]{FFCCC9}No              & \cellcolor[HTML]{FFCCC9}No      & \cellcolor[HTML]{9AFF99}{\color[HTML]{333333} Yes} \\ \bottomrule
    \end{tabularx}
\end{table}
